---
title: "HW6"
author: "Chen Mo"
date: "12/7/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

# Problem 1  

First, load and clean data.  
```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with the city of Baltimore, MD.  
```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

Create a plot shows the estimated ORs and CIs for each city.  
```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



# Problem 2

First, load and clean data.
```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
        janitor::clean_names() %>% 
        mutate(
                frace = case_when(
                        frace == 1 ~ "White",
                        frace == 2 ~ "Black",
                        frace == 3 ~ "Asian",
                        frace == 4 ~ "Puero Rican",
                        frace == 8 ~ "Other",
                        frace == 9 ~ "Unknown"
                ),
                mrace = case_when(
                        mrace == 1 ~ "White",
                        mrace == 2 ~ "Black",
                        mrace == 3 ~ "Asian",
                        mrace == 4 ~ "Puero Rican",
                        mrace == 8 ~ "Other",
                        mrace == 9 ~ "Unknown"
                ),
                malform = case_when(
                        malform == 0 ~ "absent",
                        malform == 1 ~ "present"),
                babysex = case_when(
                        babysex == 1 ~ "male",
                        babysex == 2 ~ "female"
                ),
                babysex = as_factor(babysex),
                frace = as_factor(frace),
                malform = as_factor(malform),
                mrace = as_factor(mrace)
        ) %>% 
        na.omit()
```

I use both-way stepwise method to fit a model.
```{r, include=FALSE}
model_fit = 
        lm(bwt ~ ., data = baby_df) %>% 
        step(direction='both')
```

```{r}
model_fit %>% 
        broom::tidy() %>% 
        knitr::kable()
```

by using step function in R, I fit a model using predictors shown above.  

I use R to create a plot of model residuals against fitted values.  
```{r}
baby_df %>% 
  modelr::add_residuals(model_fit) %>% 
  add_predictions(model_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
        geom_point() + 
        geom_smooth(method = "lm")
```

Then, I compare my model to two others in terms of the cross-validated prediction error.    
```{r}
model_fit =
  terms(model_fit) %>% 
  attr("term.labels") %>% 
  str_c(.,collapse = "+") %>% 
  str_c("bwt~",.) %>% 
  as.formula()
cv_df = crossv_mc(baby_df, 100)
cv_df = 
        cv_df %>% 
        mutate(
                train = map(train, as_tibble),
                test = map(test, as_tibble)
        ) %>% 
        mutate(
                md_stepwise = map(.x = train, ~ do.call("lm", list(model_fit, data = .x))),
                md_example1 = map(.x = train, ~lm(bwt ~blength + gaweeks, data = .x)),
                md_example2 = map(.x = train, ~lm(bwt ~blength * bhead *babysex, data = .x))
        ) %>% 
        mutate(
                rmse_stepwise = map2_dbl(md_stepwise, test, ~rmse(model = .x, data = .y)),
                rmse_example1 = map2_dbl(md_example1, test, ~rmse(model = .x, data = .y)),
                rmse_example2 = map2_dbl(md_example2, test, ~rmse(model = .x, data = .y)))
```

Then, I make a plot to make this comparison more straightforward.  
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

From the plots above, we can see that the model which I fit(using both-way stepwise method) has lowest RMSE compared to other two models. And the second example model has lower RMSE compared to the first example mode.  


